Event History Analyses for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-10-21 manuscript/manuscript.Rmd
update interpretation hazard results

Towards the end of the experiment (trial 1500), both congruent and incongruent primes have positive and negative effects. Positive effects are present in bins (200,240] and (240,280]. Incongruent primes again have negative effects in bins (320,360], (360,400], and (400,440], and congruent primes now also have negative effects in bins (360,400] and (400,440].
These results show that the effect of prime-target congruency changes not only on the across-bin/within-trial time scale (variable period_9), but also on the across-trial/within-experiment time scale (variable trial_c). The fact that congruent primes generate negative effects for 80 ms (compared to no-prime trials) towards the end of the experiment, while incongruent primes generate negative effects for 120 ms throughout the experiment, strongly suggests the involvement of two separate cognitive processes.

@panisWhatShapingRT2016 distinguished between response competition effects and cognitive control effects. While response competition is present in the incongruent trials throughout the experiment, @panisWhatShapingRT2016 argued that a cognitive control process is also involved, such as active top-down inhibition of the prime-triggered response. In other words, people learn that the premature prime-triggered response has to be actively inhibited in order to respond to the target stimulus. This inhibitory effect becomes visible in the congruent (compared to no-prime) trials towards the end of the experiment, while it might be masked by the inhibitory effect of response competition in the incongruent trials.

>>>>

Towards the end of the experiment (trial 1500), both congruent and incongruent primes have positive and negative effects. Positive effects are present in bins (200,240] and (240,280]. Incongruent primes again have negative effects in bins (320,360], (360,400], and (400,440], and congruent primes now also have negative effects in bins (360,400] and (400,440].
These results show that the effect of prime-target congruency changes not only on the across-bin/within-trial time scale (variable period_9), but also on the across-trial/within-experiment time scale (variable trial_c). The fact that congruent primes generate negative effects for 80 ms (compared to no-prime trials) towards the end of the experiment, while incongruent primes generate negative effects for 120 ms throughout the experiment, strongly suggests the involvement of separate cognitive processes.

@panisWhatShapingRT2016 distinguished between automatic response competition effects (bottom-up lateral inhibition between response channels), active and global inhibition effects (top-down nonselective response inhibition), and active and selective inhibition (top-down selective response inhibition). While response competition can be expected to be present in the incongruent trials throughout the experiment, active and global inhibition effects might be present in both congruent and incongruent prime trials. In other words, people learn that the prime-triggered response is premature and that they have to temporarily slow down (increase the global response threshold) in order to allow gating of the target stimulus. This global inhibitory effect might becomes visible in the congruent (compared to no-prime) trials towards the end of the experiment, while it might be masked by the automatic inhibitory effect of response competition in the incongruent trials.
